Simulating the Linux page cache in distributed applications with WRENCH

### 2020-12-10 paper_io_sim.tex

\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\english}[1]{\uwave{#1}}

@@

            We also implemented our model in WRENCH, separately from existing WRENCH components.
            We exposed page cache simulation through a user API, activated using a command-line argument.
            We used SimGrid 3.25 which is available at \url{https://framagit.org/simgrid/simgrid}.
            To implement the simulator, we used the WRENCH 1.6 version at this commit \url{https://github.com/wrench-project/wrench/tree/67185374330d2c4bf274fce222c937e838df5b03}.

\tristan{anything else interesting to mention about the implementation?}

>>>>

\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\henri}[1]{\color{green}\textbf{From Henri:}#1\color{black}}
\newcommand{\english}[1]{\uwave{#1}}

@@

            We also implemented our model as part of WRENCH, enhancing its internal implementation
            and APIs with a page cache abstraction, and allowing users to activate the feature via a
            command-line argument. For the experiments in this paper we use WRENCH 1.6 at this commit \url{https://github.com/wrench-project/wrench/tree/67185374330d2c4bf274fce222c937e838df5b03}, which uses
            SimGrid 3.25 (available at \url{https://framagit.org/simgrid/simgrid}). However, our implementation is now part of WRENCH's master branch and will be available to users with the next WRENCH release.

\tristan{anything else interesting to mention about the implementation?}
\henri{I mentioned that the implementaion is now part of the WRENCH master }
